\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-12 final/article.tex
Added all figures and algorithm

\usepackage{graphicx}

@@

@@

@@

Here we present the full approach for measuring accuracy:
\begin{itemize}
\item Select a random run not used in the training data set
\item Select a random time point in that run, and determine the (time, distance) tuple for that point in time
\item Calculate the secant line between this time point and the end of the run, the slope of which represents average pace for the rest of the run
\item Now use the SmarteRun algorithm to model a predicted run using this same time, distance, and total distance
\item Calculate the secant line between this time point and the end of the run in this predicted model, the slope of which represents predicted average pace for the rest of the run

\item Repeat this process over multiple iterations, recording both the predicted pace and actual pace for each sample. Then calculate some measure of error (such as RMSE)
\end{itemize}

>>>>

\usepackage{graphicx} 
\usepackage[]{algorithm2e}

@@

\begin{algorithm}[H]
 \KwData{Given a current time x, current distance y, and desired run distance z}

 \For{each complete run in data}{  
  \If{is one of the closest k runs}{
   include this run in $closest$
  }
 }
 \For{each run in $closest$}{  
  normalize time to [0,1] minutes\linebreak\linebreak
  calculate the weight for this run based on difference in $z$
 }
 Average all runs in $closest$ based on their weighting\linebreak\linebreak
 Rescale time from [0,1] to true time

 \caption{Computing the average predictive run}
\end{algorithm}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{overlap_run_secant.png}
\caption{A graph of pace from an actual run (shown in red) and a graph of the predicted pace (shown in blue).  The secant line pace prediction is shown for the actual and predicted run in red and blue dashed lines, respectively.}
\end{center}
\end{figure}

@@

Here we present the full approach for measuring accuracy:

\begin{algorithm}[H]
 \KwData{Given a set of complete runs $S$}

 \For{i = 0; i < 5000; i++}{  
Choose a random run $r$ in $S$\\
Choose a random (time,distance) point in $r$ as $(t,d)$\linebreak\linebreak
Calculate the true secant line $l_t$ from $(t,d)$ to the end of the run\\
Slope($l_t$) = true average pace for the rest of the run\linebreak\linebreak
Use the SmarteRun algorithm to model a predicted run using $t$, $d$, and total distance\linebreak\linebreak
Calculate the secant line $l_p$ from $(t,d)$ to the end of the predicted run\\
Slope($l_p$) = predicted average pace for the rest of the run
 }
 Calculate error between each $l_t$ and $l_p$
 \caption{Assessing the accuracy of a run prediction}
\end{algorithm}
